---
title: "individual2"
output: html_document
---

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv")
str(choco)

hist(choco$Rating)
boxplot(choco$Rating, ylab="Rating")
title("Boxplot of Chocolate Ratings")
```

There are outliers with the values 1, 1.5, 1.75, and 2.

```{r}
barplot(table(choco$Date))
```

The number of ratings increases on average every year until 2015. After 2015, the number of ratings drops below 250 and varies more than before 2015.

```{r}
plot(choco$Rating, choco$Cocoa_Percent)
cor(choco$Rating, choco$Cocoa_Percent)
```

It does not appear that chocolate ratings depend on cocoa percentage. There is no trend in the scatter plot, which indicates there is no relationship between the two. There is also a -0.15 correlation, which is very weak and suggests there is no relationship.

```{r}
best <- choco[choco$Rating >= 4,]
chars <- c(as.character(best$Characteristics1), as.character(best$Characteristics2), as.character(best$Characteristics3), as.character(best$Characteristics4))
topChars <- sort(table(chars), decreasing = TRUE)
topChars

top5Chars <- topChars[1:5]
barplot(top5Chars, ylab = "Number of Fours")
title("Top Characteristics of the Top 100 Chocolates")
```

The top three characteristics are creamy, cocoa, and nutty. Creamy was a characteristic present in 36 of the best rated chocolate. Cocoa was present in 23 of them. Nutty was present in 17 of them.