---
title: "Individual Analysis of Choco.csv"
author: "Charles Yang"
date: "9/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco)
```

### 1. Distribution of Rating
```{r}
hist(choco$Rating)
```

#### Notes
* Left skewed
  + Most chocolates have decent rating
  + Extremes taper off
```{r}
boxplot(choco$Rating, horizontal=TRUE, xlab="Rating")
title("Boxplot of Ratings")
```

#### Notes
* Most chocolates have positive rating
* Some outliers at the lower range

### 2. How do the number of ratings change per year?
```{r}
barplot(table(choco$Date))
title("Ratings per Year")
```

#### Notes
* Number of ratings increase gradually until 2015
* After 2015, number of ratings are less, but unpredictable.

### 3. Are Ratings and Cocoa_Percent correlated?
```{r}
cor(choco$Rating, choco$Cocoa_Percent)
plot(choco$Rating, choco$Cocoa_Percent)
#lm(choco$Cocoa_Percent ~ choco$Rating)
abline(77.8, -1.93)
```

#### Notes
* Graph and line of best fit do not show obvious correlation
  + Small negative relationship?
* Correlation Coefficient = -.15. Weak/Insignificant correlation.

## 4. Favorable characteristics
```{r}
top <- choco[choco$Rating >= 4,]
allCharacteristics <- c(as.character(top$Characteristics1), as.character(top$Characteristics2), as.character(top$Characteristics3), as.character(top$Characteristics4))
top10Chars <- sort(table(allCharacteristics), decreasing=TRUE)[1:10]
top10Chars
```

#### Notes
* Creamy, Cocoa, and Nutty stand out as the only double digit count in the top 100 chocolates by Rating

```{r}
barplot(top10Chars, xlab="Count", las=2, horiz=TRUE, xaxt="n")
axis(1, at=c(seq(from=0, to=35, by=5 ), 36))
title("Counts of characteristics in the top 100 chocolates")
```